# Unit Text Analysis {#sec-unit-analysis}

```{r setup, include = FALSE}
library(tidyverse)
library(tidytext)
library(SnowballC)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message= FALSE)
theme_set(theme_minimal())
```

```{r read-data, echo=FALSE, message=FALSE, warning=FALSE}
rmv_col <- function(x){
  read_csv(x) %>% 
  select(-`...1`)
}
unidata <- rmv_col("data/unidata.csv")

```


## Faculty Unit Code Analysis {#sec-unit-code}

To explore the teaching contents of Master of Data Science at Go8, an analysis based on faculty of units offered is conducted to see what components are included in this degree.

Unfortunately faculty information is not directly available on the unit handbooks, in this case, unit code is taken as a surrogate identification. As shown in the sample data below, unit code is a combination of letters and numbers, the first few characters such as FIT, MAT, usually represents the faculty this unit belongs to, we could then make relatively educated assumptions on the content of the unit. 

```{r}
unidata %>% 
  mutate(across(c(Outcomes, Overview, description), 
                ~ str_replace_all(.x, "\\\\", ""))) %>% 
  select(School, Course, Unit, Unit_code) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "condensed") %>% 
  scroll_box(height = "350px",
             width = "1250px")
```

The grouping was performed manually using the code listed below. We made certain choices though it should be noted that the grouping is not 100% accurate. For example, the code 'DATA' from the University of Sydney is all classified under IT, however, some of the units that start with DATA are taught by the faculty in the School of Mathematics and Statistics (based on personal knowledge), which means 'DATA' belongs to multiple departments. Although there would be misclassified units, the results could still provide a meaningful guidance regarding the teaching components of Master of Data Science at Go8 universities. 

```{.r}
math <- c("STAT", "MATH", "MATHS", "STATS", "MAT", "MAST", "ACTL", "QBUS")
it <- c("COMP", "FIT", "CITS", "INFS", "COSC", "CSSE", "CSYS", "EDPC", "INMT", "PHIL", "PHYS", "BUSN","DATA", "INFO", "INFS")
commerce <- c("ECON", "FINS", "MARK", "ACCT", "FINM", "MGMT", "MKTG")
spatial <- c("GEOM", "ITLS")
science <- c("EDUC", "SCIE", "SOCR")
health <- c("BINF", "BMS", "HTIN", "PUBH")
```

It is clear from @fig-unitcode that IT and Stat/Math are the two dominating components in the Master of Data Science degrees at Go8. Most units (165 out of 298) fall under the IT faculty, followed by Math and Stats, which has 79 units.

```{r echo=FALSE}
math <- c("STAT", "MATH", "MATHS", "STATS", "MAT", "MAST", "ACTL", "QBUS")
it <- c("COMP", "FIT", "CITS", "INFS", "COSC", "CSSE", "CSYS", "EDPC", 
        "INMT", "PHIL", "PHYS", "BUSN","DATA", "INFO", "INFS")

commerce <- c("ECON", "FINS", "MARK", "ACCT", "FINM", "MGMT", "MKTG")
spatial <- c("GEOM", "ITLS")
science <- c("EDUC", "SCIE", "SOCR")
health <- c("BINF", "BMS", "HTIN", "PUBH")

comp <- unidata %>% 
  mutate(group = str_extract(Unit_code, "[A-Za-z]+")) %>% 
  group_by(School) %>% 
  count(group, sort = T) %>% 
  ungroup() %>% 
  mutate(category = case_when(group %in% it ~ "IT",
                              group %in% math ~ "Stat/Math",
                              group %in% commerce ~ "Commerce",
                              group %in% spatial ~ "Spatial",
                              group %in% science ~ "Science/Social Science",
                              group %in% health ~ "Health/Bioinfo/Biostat")) %>% 
  mutate(category = if_else(is.na(category), "Other", category))
```

```{r fig-unitcode, fig.cap = "Teaching Content by Faculty"}
comp %>% 
  mutate(category = fct_reorder(category, n, sum)) %>% 
  ggplot(aes(x = n,
             y = category,
             fill = category)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "",
       y = "",
       title = "Teaching Content by Faculty") +
  theme(legend.position = "none")
```

Similar findings could be observed from some but not all Go8 universities. @fig-tile shows a heat map of the faculty breakdown by university. Since the total number of units offered by each university is different, instead of showing the actual number, proportions are plotted to make better comparisons across universities. 

```{r fig-tile, fig.cap = "Proportion of IT Units Varys Across Go8 Universities"}
comp %>% 
  group_by(School) %>% 
  mutate(prop = round(n/sum(n),4)*100) %>% 
  ungroup() %>% 
  group_by(School, category) %>% 
  summarise(prop_sum = sum(prop)) %>% 
  ungroup() %>% 
  ggplot(aes(x = School, y = category, fill = prop_sum)) +
  geom_tile(color = "white",
            lwd = 1.5,
            linetype = 1) +
  geom_text(aes(label = prop_sum), color = "white", size = 4) +
  coord_fixed() +
  labs(y = "",
       title = "Proportion of IT Units Varys Across Go8 Universities",
       fill = "% of total units")
```

Lighter colour represents higher proportion, it is obvious that at Monash University (monash), University of Adelaide (Uuade), University of Sydney (usyd) and University of Western Australia (uwa), units from IT faculty occupies more than 50% of the total units offered, especially at Monash University, the proportion of IT units nearly reaches 87%. 

On the other hand, University of Melbourne (unimelb) and University of Queensland (uq) offers relatively higher proportion of statistical and mathematical (Stat/Math) units, almost the same percentage as IT units. Whereas units offered at the Australian National University (anu) and UNSW Sydney (unsw) are more evenly distributed across IT, Stat/Math, Science/Social Science and Commerce respectively.

In addition, it is also clear that units offered at University of Melbourne (unimelb), University of Queensland (uq) and University of Western Australia (uwa) covers five out of eight categories, which implies the Master of Data Science degrees at these three universities provide more varieties in terms of units offered.

Based on the findings above, it seems that there is a shared structure across Go8 that Master of Data Science is a IT based, computational degree, but the proportion it occupies varies by universities. Monash University tends to be heavily focused on IT and computational aspects, whereas the Master of Data Science degree at UNSW Sydney and ANU are more balanced across IT, statistics and math, as well as science and commerce.

## Unit Overview and Learning Outcome - Bigram {#sec-unit-bigram}

After having a rough idea of the bigger picture, we then moved to explore what exactly are the teaching contents. Single word analysis, bigram and trigram are all produced in order to identify the frequently mentioned words and/or terms. Words are first stemmed in the pre-processing stage, `distinct` function is then applied to units and terms, so that same words or terms are only counted once in a unit to avoid duplicated counting. Words and terms such as 'student', 'successful completion' add more noises than values to the results, are removed in the pre-processing step.

The bigram, shown in @fig-bigram below provides the most informative results among the n-gram analysis. Machine learning (machin learn) appears quite often, as well as software development (softwar develop), linear model, statistical analysis (statist analysi), spatial data. It seems that these frequently mentioned terms are associated with both computational and statistical concepts and skills, which aligns with the findings from the unit code analysis in previous section.

```{r echo=FALSE, warning=FALSE}
unidata_bigram <- unidata %>% 
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>% 
  separate(bigram,
           into = c("word1", "word2"),
           sep = " ") %>% 
  filter(!word1 %in% stop_words$word & !word2 %in% stop_words$word) %>%  
  filter(!word1 %in% c("content","topic", "unit", "subject", "final", "capstone", "involve", "project", "master", "practical", "programming") & 
         !word2 %in% c("student", "skill", "set", "piece", "concept", "capstone", "delivery", "domain", "manner", "due", "range", "unit", "master")) %>% 
  subset(!grepl("[0-9]", word1)) %>% 
  subset(!grepl("[0-9]", word2)) %>% 
  mutate(word1_stem = wordStem(word1, language = "english"),
         word2_stem = wordStem(word2, language = "english")) %>% 
  mutate(word = as_factor(paste(word1_stem, word2_stem, sep = " "))) %>%
  #filter(!word == "data science") %>% 
  distinct(School, Unit, word) %>% 
  group_by(School) %>% 
  count(word, sort = TRUE) %>% 
  ungroup()
```

```{r fig-bigram, fig.cap = "Unit Overview and Learning Outcome - Bigram (n > 4)"}
unidata_bigram %>% 
  filter(n > 4) %>% 
  mutate(word = fct_reorder(word, n, sum))%>% 
  ggplot(aes(x=n,
             y = word))+
  geom_col(fill = "#006DAE")+
  #scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "bottom") +
  labs(y = "",
       fill = "Category",
       title = "Unit Overview and Learning Outcome - Bigram (n > 4)") +
  scale_x_continuous(expand = c(0, 0.1))
```

Unfortunately, due to the limited number of observations in the collected data set, the count for each term is too low to make meaningful interpretations or justifications. In addition, similar terms such as research findings, research designs and research literature are supposed to be grouped and counted together, but are not in the bigram. This issue is later solved by introducing the topic modeling technique for natural language processing, which will be discussed in Section @sec-topicmod.
